A cautionary note on the use of Ornstein Uhlenbeck models in macroevolutionary studies

### 2015-05-11 Manuscript/ohyou.tex
Removed abstract word count

\section{Abstract 100-200}
  Phylogenetic comparative methods are increasingly used to give new insights into the causes and consequences of trait variation among species. 
  The foundation of these methods is a suite of models that attempt to capture evolutionary patterns by extending the Brownian constant variance model. 
  However, the properties of these models are often poorly understood which can lead to the misinterpretation of results.
  Here we focus on one of these models - the Ornstein-Uhlenbeck (OU) model. 
  We introduce the model, its general properties and some issues with its use in ecology, evolution and palaeontology.
  Using simulations, we demonstrate the inherent bias in estimating the core parameter of the OU model, $\alpha$, especially where datasets are small. 
  We also show that very small amounts of error in data can have profound effects on the performance of OU models.
  Finally, we make recommendations for best practice in fitting OU models in phylogenetic comparative analyses, and for interpreting the $\alpha$ parameter.

>>>>

\section{Abstract}
  Phylogenetic comparative methods are increasingly used to give new insights into the causes and consequences of trait variation among species. 
  The foundation of these methods is a suite of models that attempt to capture evolutionary patterns by extending the Brownian constant variance model. 
  However, the properties of these models are often poorly understood which can lead to the misinterpretation of results.
  Here we focus on one of these models - the Ornstein-Uhlenbeck (OU) model. 
  We introduce the model, its general properties and some issues with its use in ecology, evolution and palaeontology.
  Using simulations, we demonstrate the inherent bias in estimating the core parameter of the OU model, $\alpha$, especially where datasets are small. 
  We also show that very small amounts of error in data can have profound effects on the performance of OU models.
  Finally, we make recommendations for best practice in fitting OU models in phylogenetic comparative analyses, and for interpreting the $\alpha$ parameter.
